
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     PROFESSIONAL EXPERIENCE
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Professional Experience}

%\runsubsection{UI for BIMSurfer}
%\descript{| Virtual Reality Project 1}
%\location{Feb. 2017 – Mar. 2017 | Ecole Centrale de Nantes, Nantes, France}
%\vspace{\topsep} % Hacky fix for awkward extra vertical space
%\begin{tightemize}
%\item Matching of photographs of a building with its BIM model
%\item Implementing methods in JavaScript to improve UI
%\item Installing OpenCV Python for Image Processing
%\end{tightemize}
%\sectionsep

%\runsubsection{UI for the 3D map in Unity}
%\descript{| Virtual Reality Project 2}
%\location{Oct. 2016 – Jan. 2017 | Ecole Centrale de Nantes, Nantes, France}
%\begin{tightemize}
%\item Designing of an user interface on the multi-touch screen
%\item Construction of a functional and applicable plug-in
%\item Manipulation of the 3D model of Nantes in 1900 
%\end{tightemize}
%\sectionsep

\runsubsection{Fraunhofer Institute IAIS}
\descript{| PhD Partner}
\location{Sept. 2020 -| Bonn}
\begin{tightemize}
    \item Partnership with the University of Bonn
\end{tightemize}
\sectionsep

\runsubsection{\href{http://www.datastadium.co.jp/en/}{DATA Stadium Inc.}}
\descript{| Part-time job}
\location{Mar. – June 2019| Akasaka, Tokyo}
\begin{tightemize}
    \item Analysis of space using Voronoi diagrams and empty circles
\end{tightemize}
\sectionsep

\runsubsection{Weber State University} \descript{| Scholarly Exchange} 
\location{Oct. - Dec. 2019 | Utah}
\begin{tightemize}
\item Machine Learning and Causal Inference for NBA games
\item Data Coding for researches of supply chain management
    \end{tightemize}
\sectionsep

\runsubsection{Tinder}
\descript{| Internship}
\location{Mar. - June 2019| Tokyo}
\begin{tightemize}
\item Market research, Industry analysis
\item Data research and analysis
\item Planning, execution and analysis of marketing strategy
\item Management of Tinder’s official social media and overall admin work
\end{tightemize}
\sectionsep

\runsubsection{Nomura Securities Co., Ltd.}
\descript{| Internhship}
\location{Nov. - Dec. 2018| Otemachi, Tokyo}
\begin{tightemize}
\item Economic Analysis using the social network analysis
\end{tightemize}
\sectionsep

\runsubsection{Intel Corporation}
\descript{| Internhship}
\location{Oct. – Nov. 2018| Yurakucho, Tokyo}
\begin{tightemize}
\item Making a deep learning demo using OpenVINO and OpenCV
\item Attending sales and marketing meeting 
\end{tightemize}
\sectionsep

\newpage

\runsubsection{NAVITIME JAPAN Co., Inc.}
\descript{| Internhship}
\location{Sep. – Oct. 2018| Aoyama, Tokyo}
\begin{tightemize}
\item Analysing traffic data as a traffic consultant using Python
\end{tightemize}
\sectionsep

\runsubsection{Future Architect, Inc.}
\descript{| Internhship}
\location{Aug. 2018| Osaki, Tokyo}
\begin{tightemize}
\item Maneuvering a Roomba using Robot Operating System in Python and Hololens
\end{tightemize}
\sectionsep

\runsubsection{\href{https://www.skillupai.com/}{SkillUP AI Inc.}}
\descript{| Outsourcing contract}
\location{May 2018 – | Shibuya, Tokyo}
\begin{tightemize}
\item Giving a course of Python and Mathematics for Machine Learning
\end{tightemize}
\sectionsep

\runsubsection{Johnson Controls Industries}
\descript{| Internship}
\location{May - August 2017 | Carquefou, France}
\begin{tightemize}
\item Development of a Microsoft Hololens application
\end{tightemize}
\sectionsep

\runsubsection{Institut Mutualiste de Montsouris}
\descript{| Internship}
\location{July 2016 | Biomedical service, Montsouris, Paris}
\begin{tightemize}
\item Management of maintenance of medical devices with nine people
\item Development of a maintenance database (Excel VBA)
\end{tightemize}
\sectionsep

\vspace{3mm}
